---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Heather Hawkins"
date: "01-31-23"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
library(tidyverse)
library(skimr)
#install.packages("devtools")
#devtools::install_github("rstudio-education/dsbox")
```

```{r load-data, message = FALSE}
library(readr)
states <- read_csv("data/states.csv")
```

### Exercise 1

```{r read-row-col-dennys}
nrow(dennys)
ncol(dennys)
```
There are 1643 rows and 6 columns for the Denny's data. The 6 rows represent the address, city, state, zip code, longitude, and latitude, while the rows represent each denny's location. 

### Exercise 2

```{r read-row-col-laquinta}
nrow(laquinta)
ncol(laquinta)
```
There are 909 rows and 6 columns for the La Quinta data. The 6 rows represent the address, city, state, zip code, longitude, and latitude, while the rows represent each La Quinta location. 

### Exercise 3

...

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

 
Add exercise headings as needed.

