---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Heather Hawkins"
date: "01-31-23"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
library(tidyverse)
library(skimr)
#install.packages("devtools")
#devtools::install_github("rstudio-education/dsbox")
```

```{r load-data, message = FALSE}
library(readr)
states <- read_csv("data/states.csv")
```

### Exercise 1

```{r read-row-col-dennys}
nrow(dennys)
ncol(dennys)
```
There are 1643 rows and 6 columns for the Denny's data. The 6 rows represent the address, city, state, zip code, longitude, and latitude, while the rows represent each denny's location. 

### Exercise 2

```{r read-row-col-laquinta}
nrow(laquinta)
ncol(laquinta)
```
There are 909 rows and 6 columns for the La Quinta data. The 6 rows represent the address, city, state, zip code, longitude, and latitude, while the rows represent each La Quinta location. 

### Exercise 3
Yes, La Quinta also has locations in Canada, Mexico, China, New Zealand,Turkey, UAE, Chile, and Colombia. 

Denny's only has locations in the USA
...

### Exercise 4

Filtering out locations that are not in the state data. If they are in the US, they would be in the data set. 


...

### Exercise 5


```{r denny-us-filter}
dennys %>%
  filter(!(state %in% states$abbreviation))
```
None found, all Denny's are in the US
5
### Exercise 6


```{r dn-us}
dennys %>% 
  mutate(country = "United States")
```

###Exercise 7


14 La Quintas are outside of the usa. 

```{r Laquinta-country}
laquinta %>%
  filter(!(state %in% states$abbreviation))
```
Colombia (ANT)
Mexico (VE, AG, CH, NL, PU, SLP, QR)
Canada (ON, BC)
Honduras (FM)


###Exercise 8

Adding country variable to the La Quinta dataset 

``` {r LQ-NUSA}
laquinta <- laquinta %>%
  mutate(country = case_when(
    state %in% state.abb     ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    state == "FM"      ~ "Honduras", 
    state %in% c("AG", "QR", "CH", "NL", "VE", "PU", "SL") ~ "Mexico"
  ))

laquinta <- laquinta %>%
  filter(country == "United States")
```


###Exercise 9 


```{r count-states}
dennys %>%
  dplyr::count(state) %>%
  inner_join(states, by = c("state" = "abbreviation"))

laquinta %>%
  dplyr::count(state) %>%
  inner_join(states, by = c("state" = "abbreviation"))
```

Which states have the most and fewest Denny’s locations? 

MOst= Califorina
Least= Delaware

What about La Quinta? 
Most= Texas
Least= Maine

Is this surprising? Why or why not?

It is suprising that Texas and California dont have the most of both. Since both CA and TX have plenty of land and also a large population, it is suprising that they are not both similar in number for both La Quintas and Denny;s

###Exercise 10

Which states have the most Denny’s locations per thousand square miles? What about La Quinta?
Next, we put the two datasets together into a single data frame. However before we do so, we need to add an identifier variable. We’ll call this establishment and set the value to "Denny's" and "La Quinta" for the dn and lq data frames, respectively.


``` {r La-Dn}
dn <- dennys %>%
  mutate(establishment = "Denny's")
lq <- laquinta %>%
  mutate(establishment = "La Quinta")

dn_lq <- bind_rows(dn, lq)
```

We can plot the locations of the two establishments using a scatter plot, and color the points by the establishment type. Note that the latitude is plotted on the x-axis and the longitude on the y-axis.
```{r Plot Location Data}
ggplot(dn_lq, mapping = aes(x = longitude,
                            y = latitude,
                            color = establishment)) +
  geom_point(alpha= .5)

```

###Exercise 11

```{r NC Locations}
nc <- dn_lq %>%
  filter(state =="NC")
ggplot(nc, mapping = aes(x = longitude,
                            y = latitude,
                            color = establishment)) +
  geom_point(alpha=.7)+
  scale_color_manual(values=c("orange", "green"))+
  theme_dark()+
  labs(title="North Carolina's Denny's and La Quinta Locations", color ="Establishment")+
  ylab("Latitude")+
  xlab("Longitude")
```

Visually, does Mitch Hedberg’s joke appear to hold here?

Not really, There are not many Denny's next to Laquintas in NC

###Exercise 12

```{r Texasdn-la}
tx <- dn_lq %>%
  filter(state =="TX")
ggplot(tx, mapping = aes(x = longitude,
                            y = latitude,
                            color = establishment)) +
  geom_point(alpha=.7)+
  scale_color_manual(values=c("orange", "green"))+
  theme_dark()+
  labs(title="Texas' Denny's and La Quinta Locations", color ="Establishment")+
  ylab("Latitude")+
  xlab("Longitude")
```
Visually, does Mitch Hedberg’s joke appear to hold here?

Definitely, There seems to be alot of Denny's near La Quintas in Texas (probably bc there are so many La Quintas)