---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Heather Hawkins"
date: "01-31-23"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
library(tidyverse)
library(skimr)
#install.packages("devtools")
#devtools::install_github("rstudio-education/dsbox")
```

```{r load-data, message = FALSE}
library(readr)
states <- read_csv("data/states.csv")
```

### Exercise 1

```{r read-row-col-dennys}
nrow(dennys)
ncol(dennys)
```
There are 1643 rows and 6 columns for the Denny's data. The 6 rows represent the address, city, state, zip code, longitude, and latitude, while the rows represent each denny's location. 

### Exercise 2

```{r read-row-col-laquinta}
nrow(laquinta)
ncol(laquinta)
```
There are 909 rows and 6 columns for the La Quinta data. The 6 rows represent the address, city, state, zip code, longitude, and latitude, while the rows represent each La Quinta location. 

### Exercise 3
Yes, La Quinta also has locations in Canada, Mexico, China, New Zealand,Turkey, UAE, Chile, and Colombia. 

Denny's only has locations in the USA
...

### Exercise 4

Filtering out locations that are not in the state data. If they are in the US, they would be in the data set. 


...

### Exercise 5


```{r denny-us-filter}
dennys %>%
  filter(!(state %in% states$abbreviation))
```
None found, all Denny's are in the US
5
### Exercise 6


```{r dn-us}
dennys %>% 
  mutate(country = "United States")
```

###Exercise 7


14 La Quintas are outside of the usa. 

```{r Laquinta-country}
laquinta %>%
  filter(!(state %in% states$abbreviation))
```
Colombia (ANT)
Mexico (VE, AG, CH, NL, PU, SLP, QR)
Canada (ON, BC)
Honduras (FM)


###Exercise 8

Adding country variable to the La Quinta dataset 

``` {r LQ-NUSA}
laquinta <- laquinta %>%
  mutate(country = case_when(
    state %in% state.abb     ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    state == "FM"      ~ "Honduras", 
    state %in% c("AG", "QR", "CH", "NL", "VE", "PU", "SL") ~ "Mexico"
  ))

laquinta <- laquinta %>%
  filter(country == "United States")
```


###Exercise 9 


```{r count-states}
dennys %>%
  dplyr::count(state) %>%
  inner_join(states, by = c("state" = "abbreviation"))

laquinta %>%
  dplyr::count(state) %>%
  inner_join(states, by = c("state" = "abbreviation"))
```

Which states have the most and fewest Denny’s locations? 

MOst= Califorina
Least= Delaware

What about La Quinta? 
Most= Texas
Least= Maine

Is this surprising? Why or why not?


###Exercise 10

Which states have the most Denny’s locations per thousand square miles? What about La Quinta?
Next, we put the two datasets together into a single data frame. However before we do so, we need to add an identifier variable. We’ll call this establishment and set the value to "Denny's" and "La Quinta" for the dn and lq data frames, respectively.

dn <- dn %>%
  mutate(establishment = "Denny's")
lq <- lq %>%
  mutate(establishment = "La Quinta")
Because the two data frames have the same columns, we can easily bind them with the bind_rows function:

dn_lq <- bind_rows(dn, lq)
We can plot the locations of the two establishments using a scatter plot, and color the points by the establishment type. Note that the latitude is plotted on the x-axis and the longitude on the y-axis.

ggplot(dn_lq, mapping = aes(x = longitude,
                            y = latitude,
                            color = establishment)) +
  geom_point()
The following two questions ask you to create visualizations. These visualizations should follow best practices you learned in class, such as informative titles, axis labels, etc. See http://ggplot2.tidyverse.org/reference/labs.html for help with the syntax. You can also choose different themes to change the overall look of your plots, see http://ggplot2.tidyverse.org/reference/ggtheme.html for help with these.

###Exercise 11

Filter the data for observations in North Carolina only, and recreate the plot. You should also adjust the transparency of the points, by setting the alpha level, so that it’s easier to see the overplotted ones. Visually, does Mitch Hedberg’s joke appear to hold here?

###Exercise 12

Now filter the data for observations in Texas only, and recreate the plot, with an appropriate alpha level. Visually, does Mitch Hedberg’s joke appear to hold here?